18th International Satisfiability Modulo Theories Competition (SMT-COMP 2023): Rules and Procedures

### 2023-04-26 rules/rules23.tex
SMT-COMP23 rules: changes to the wall-clock and CPU time scores for the incremental track.

\header{Wall-Clock Time Score ($\mathbf{w}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the wall-clock time score $w$ is the same as 
the actual (real-valued) wall-clock time $\it{aw}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $T$, i.e., 
$w = 0$ if $e = 1$, the process did not terminate within the time limit $T$, or 
it did return unknown or an unknown result.
For the \inctrack, the wall-clock time score $w$ 
is the (real-valued) wall-clock time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
this means especially that $w = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.

@@

\header{CPU Time Score ($\mathbf{c}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the CPU time score $c$ is the same as 
the actual (real-valued) CPU time $\it{ac}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $mT$, i.e., 
$c = 0$ if $e = 1$, the process did not terminate within the time limit $mT$, or 
it did return unknown or an unknown result.
For the \inctrack, the CPU time score $c$ 
is the (real-valued) CPU time in seconds until the process returned the last correct result for a \akey{check-sat} command within the time limit;
this means especially that $c = 0$ is zero if no (correct) result was returned for the first \akey{check-sat} command within the time limit.

>>>>

\header{Wall-Clock Time Score ($\mathbf{w}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the wall-clock time score $w$ is the same as 
the actual (real-valued) wall-clock time $\it{aw}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $T$, i.e., 
$w = 0$ if $e = 1$, the process did not terminate within the time limit $T$, or 
it did return unknown or an unknown result.
For the \inctrack, the wall-clock time score $w$ 
is the (real-valued) wall-clock time in seconds until the process returned the last time sat/unsat within the time limit;
this means especially that $w = 0$ if the process never returned sat/unsat within the time limit.

@@

\header{CPU Time Score ($\mathbf{c}$).}
For the \maintrack, \ucoretrack, \mvaltrack, \paralleltrack, and
\cloudtrack, the CPU time score $c$ is the same as 
the actual (real-valued) CPU time $\it{ac}$, 
except that it is zero if the benchmark was not correctly solved within the time limit $mT$, i.e., 
$c = 0$ if $e = 1$, the process did not terminate within the time limit $mT$, or 
it did return unknown or an unknown result.
For the \inctrack, the CPU time score $c$ 
is the (real-valued) CPU time in seconds until the process returned the last time sat/unsat within the time limit;
this means especially that $c = 0$ if the process never returned sat/unsat within the time limit.
